\textbf{Acknowledgment}

This document describes about the Sixth version of Minimal Advanced
Treatments of Surface Interaction and RunOff (MATSIRO) model, which is
implemented in MIROC6 climate model. The original document was written
in 2001 by Dr.~Seita Emori in Japanese about the very first version of
MATSIRO, which was implemented in CCSR/NIES AGCM5. There has been no
update since then, even though there are significant updates in the
model itself. Furthermore, thinking about Integrated Land Simulator or
ILS, the new framework of land model, which adopts MATSIRO as a part of
physical model components, it is highly needed to make efficient ways to
update the document by community effort. These are the main motivations
of making this document.

To update the description, we organized MATSIRO6 document writing team
in the summer of 2020. Furthermore, it was decided to utilize Github
version management platform to maintain the documentation by the team.
The team consists of two groups; the authors and the
supervisors/editors. All of the authors are doctor course students of
Global Hydrology Group of the University of Tokyo, who use or are
interested in using MATSIRO6, and the supervisors/editors are
researchers, who contributed to development of MATSIRO6 and/or its
previous versions.

The original Japanese document written by Dr.~Emori is in LaTeX format
and there was English translated document done by Dr.~Hanasaki and
Dr.~Hijioka in MS Word format. It was needed to make the document into
Markdown format from these two files. This part was mainly done by
Ms.~Kanon Kino. Then the team was divided into several groups, and each
group became in charge of each section. These groups and corresponding
sections are as follows:

\begin{itemize}
\item
  Mr.~Akira Takeshima supervised by Dr.~Yukihiko Onuma for Snow (Ch.8)
\item
  Mr.~Shuping Li supervised by Dr.~Natsuki Yoshida for Runoff (Ch.9)
\item
  Ms.~Kanon Kino supervised by Dr.~Tatsuo Suzuki for Lake (Ch.11)
\item
  Mr.~Qiang Guo supervised by Dr.~Yusuke Satoh for Wetland (Ch.12)
\end{itemize}

Later, in addition to the sections above, it was realized that some
sections needed more amendments and help, so that following additional
assignments were conducted.

\begin{itemize}
\item
  Dr.~Tomoko Nitta for Prognostic Variables (Ch.1.2)
\item
  Mr.~Shuping Li for Tile scheme (Ch.13)
\item
  Mr.~Qiang Guo for Physical Formulation and Process in Lake (Ch.11.4)
\item
  Dr.~Tomoko Nitta for Lake-river Coupling (Ch.11.5)
\end{itemize}

It took about five months to draft, and the whole draft was reviewed by
all supervisors/editors. At last, the rest of the sections were amended
and improved by all.

The team thanks the support of ``Integrated Research Program for
Advancing Climate Models (TOUGOU Program)'' from the Ministry of
Education, Culture, Sports, Science, and Technology (MEXT), Japan.
Finally, the team would sincerely express our respect to Dr.~Seita
Emori, the first developer of the model and the author of the original
version of this document.

\begin{flushright}

Kei Yoshimura

lead member of the team

March 31, 2021
\end{flushright}
