\hypertarget{ux53c2ux8003ux6587ux732e}{%
\subsection{参考文献}\label{ux53c2ux8003ux6587ux732e}}

\begin{itemize}
\item
  Ball, J. T., 1988: An analysis of stomatal conductance. Ph.D.~thesis,
  Stanford University, 89 pp.
\item
  Beven, K. J., and M. J. Kirkby, 1979: A physically based variable
  contributing area model of basin hydrology, {Hydrol. Sci. Bull.},
  {\textbf{24}}, 43--69.
\item
  Clapp, R. B., and G. M. Hornberger, 1978: Empirical equations for some
  soil hydraulic properties. {Water Resour. Res.}, {\textbf{14}},
  601--604.
\item
  Collatz, G. J., J. A. Berry, G. D. Farquhar, and J. Pierce, 1990: The
  relationship between the Rubisco reaction mechanism and models of leaf
  photosynthesis. {Plant Cell Environ.}, {\textbf{13}}, 219--225.
\item
  Collatz, G. J., J. T. Ball, C. Grivet, and J. A. Berry, 1991:
  Physiological and environmental regulation of stomatal conductance,
  photosynthesis and transpiration: A model that includes a laminar
  boundary layer. {Agric. For. Meteor.}, {\textbf{54}}, 107--136.
\item
  Collatz, G. J., M. Ribas-Carbo, and J. A. Berry, 1992: Coupled
  Photosynthesis-Stomatal Conductance Model for leaves of TERM00000
  plants. {Aust. J. Plant. Physiol.}, {\textbf{19}}, 519--538.
\item
  Farquhar, G. D., S. von Caemmerer, and J. A. Berry, 1980: A
  biochemical model of photosynthetic TERM00001 fixation in leaves of
  TERM00002 species. {Planta}, {\textbf{149}}, 78--90.
\item
  Kondo, J., and T. Watanabe, 1992: Studies on the bulk transfer
  coefficients over a vegetated surface with a multilayer energy budget
  model. {J. Atmos. Sci}, {\textbf{49}}, 2183--2199.
\item
  Rutter, B., A. J. Morton, and P. C. Robins, 1975: A predictive model
  of rainfall interception in forests. II. Generalization of the model
  and comparison with observations in some coniferous and hardwood
  stands. {J. Appl. Ecol.}, {\textbf{12}}, 367--380.
\item
  Sellers, P. J., D. A. Randall, G. J. Collatz, J. A. Berry, C. B.
  Field, D. A. Dazlich, C. Zhang, G. D. Collelo, and L. Bounoua, 1996: A
  revised land surface parameterization (SiB2) for atmospheric GCMs.
  Part I: Model formulation. {J. Climate}, {\textbf{9}}, 676--705.
\item
  Sivapalan, M., K. Beven, and E. F. Wood, 1987: On hydrologic
  similarity. 2, A scaled model of storm runoff production. {Water
  Resour. Res}, {\textbf{23}}, 2266--2278.
\item
  Stieglitz, M., D. Rind, J. Famiglietti, and C. Rosenzweig, 1997: An
  efficient approach to modeling the topographic control of surface
  hydrology for regional and global climate modeling. {J. Climate},
  {\textbf{10}}, 118--137.
\item
  Watanabe, T., 1994: Bulk parameterization for a vegetated surface and
  its application to a simulation of nocturnal drainage flow.
  {Boundary-Layer Met.}, {\textbf{70}}, 13--35.
\item
  Wiscombe, W. J., and S. G. Warren, 1980: A model for the spectral
  albedo of snow. I. Pure snow. {J. Atmos. Sci.}, {\textbf{37}},
  2712--2733.
\item
  渡辺力・大谷義一, 1995: キャノピー層内の日射量分布の近似計算法.
  {農業気象}, {\textbf{51}}, 57--60.
\end{itemize}
